---
title: "Bayesian-Inference"
author: "Samantha-Jo Caetano"
date: "February 10 or 11 2021"
output: pdf_document
---

```{r load-tidy-121341,message=FALSE,warning=FALSE}
library(tidyverse)
library(patchwork)
```

# Introduction to Bayesian Inference

With repeated flipping in the Bayesian setting, with our prior distribution on $\theta$ described in the slides, we would form the posterior distribution as follows:

$$
p(\theta|X) = \frac{\theta^{\sum_{i=1}^{n}x_{i}}(1-\theta)^{n - \sum_{i=1}^{n}x_{i}}\times 0.2^{I(\theta = 0.7)}0.8^{I(\theta = 0.3)}}{\sum_{\theta = 0.3,0.7}\theta^{\sum_{i=1}^{n}x_{i}}(1-\theta)^{n - \sum_{i=1}^{n}x_{i}}\times 0.2^{I(\theta = 0.7)}0.8^{I(\theta = 0.3)}}
$$

### Visualization

It is helpful to visualize the prior and posterior, for the observed data. Because both prior and posterior only allow two values, we can do this using a simple bar chart:

```{r binomial-vis1}
visualize_binomial_priorposterior <- function(sumx,n) {
  prior <- function(theta) {
    if (theta == .3) {
      return(.8)
    }
    else if (theta == .7) {
      return(.2)
    }
    0
  }
  likelihood <- function(theta) theta^sumx * (1-theta)^(n - sumx)
  marginal_likelihood <- prior(.7) * likelihood(.7) + prior(.3) * likelihood(.3)
  posterior <- function(theta) likelihood(theta) * prior(theta) / marginal_likelihood
  
  # Plot of the prior and posterior distributions for these observed data
  tibble(
    theta = c(.3,.7,.3,.7),
    value = c(prior(.3),prior(.7),posterior(.3),posterior(.7)),
    type = c("Prior","Prior","Posterior","Posterior")
  ) %>%
    ggplot(aes(x = theta,y = value,fill = type)) +
    theme_classic() + 
    geom_bar(stat = "identity",position = "dodge",colour = "black") +
    labs(title = "Prior and Posterior for theta",
         subtitle = str_c("Observed data: ",sumx," flips in ",n," throws"),
         x = "Theta, probability of heads",
         y = "Prior/Posterior Probability",
         fill = "") +
    scale_x_continuous(breaks = c(0.30,0.70),labels = c("0.30","0.70")) +
    scale_y_continuous(labels = scales::percent_format()) +
    scale_fill_brewer(palette = "Reds")
  
}
```

Plotting is nice as it lets us compare how different observed data, and different experiments (number of throws) affect the prior/posterior balance of belief:

```{r binomial-vis2,fig.height=10}
# library(patchwork)
(visualize_binomial_priorposterior(6,6) | visualize_binomial_priorposterior(6,10)) /
(visualize_binomial_priorposterior(6,20) | visualize_binomial_priorposterior(6,50)) /
(visualize_binomial_priorposterior(0,10) | visualize_binomial_priorposterior(1,10)) /
(visualize_binomial_priorposterior(7,10) | visualize_binomial_priorposterior(10,10))
```
